---
title: "Delhi Regression Tuning 11.12.15"
author: "Michael Murray"
date: "November 12, 2015"
output: word_document
---

```{r, echo=FALSE}
setwd("~/Spatial Segmentation/India")
delhi <- read.csv("delhi.csv")
```

### Standard Regression with a dummy variable for large ( > 500 units) buildings
#### Large buildings appear to be a large amenity
```{r}
head(delhi$large.building)
delhi.lm.poi <- lm(hp ~ rooms + property + Connaught.Place + Nehru.Place + Laxmi.Nagar +airport + bar + cemetery + golf + industrial +
                     parking + petrol + tourist + amusement + bus +
                     community + highered + library + parkinglot +
                     train + police + animal + business + commuterrail +
                     hospital + performingarts + school + park + large.building, data = delhi)

summary(delhi.lm.poi)
```

### Remove CBD3/Laxmi Nagar because it was showing up as a disamenity
#### Removal causes Nehru Place to appear as a disamenity
```{r}
delhi.lm.poi2 <- lm(hp ~ rooms + property + Connaught.Place + Nehru.Place +
                     airport + bar + cemetery + golf + industrial +
                     parking + petrol + tourist + amusement + bus +
                     community + highered + library + parkinglot +
                     train + police + animal + business + commuterrail +
                     hospital + performingarts + school + park + large.building, data = delhi)

summary(delhi.lm.poi2)

anova(delhi.lm.poi,delhi.lm.poi2)
```

### Using VIF, aside from the CBDs - airport, animal, and performingarts contribute the most to multicollinearity
### Without "animal"
```{r}
delhi.lm.poi3 <- lm(hp ~ rooms + property + Connaught.Place + Nehru.Place + Laxmi.Nagar + airport + bar + cemetery + golf + industrial +
                     parking + petrol + tourist + amusement + bus +
                     community + highered + library + parkinglot +
                     train + police + business + commuterrail +
                     hospital + performingarts + school + park + large.building, data = delhi)

summary(delhi.lm.poi3)
```
#### without "performingarts"
```{r}
delhi.lm.poi4 <- lm(hp ~ rooms + property + Connaught.Place + Nehru.Place + Laxmi.Nagar + airport + bar + cemetery + golf + industrial +
                     parking + petrol + tourist + amusement + bus +
                     community + highered + library + parkinglot +
                     train + police + animal + business + commuterrail +
                     hospital + school + park + large.building, data = delhi)
summary(delhi.lm.poi4)
```
#### without "airport"
```{r}
delhi.lm.poi5 <- lm(hp ~ rooms + property + Connaught.Place + Nehru.Place + Laxmi.Nagar + bar + cemetery + golf + industrial +
                     parking + petrol + tourist + amusement + bus +
                     community + highered + library + parkinglot +
                     train + police + animal + business + commuterrail +
                     hospital + performingarts + school + park + large.building, data = delhi)

summary(delhi.lm.poi5)
```
#### without all three
```{r}
delhi.lm.poi6 <- lm(hp ~ rooms + property + Connaught.Place + Nehru.Place + Laxmi.Nagar + bar + cemetery + golf + industrial +
                     parking + petrol + tourist + amusement + bus +
                     community + highered + library + parkinglot +
                     train + police + business + commuterrail +
                     hospital + school + park + large.building, data = delhi)

summary(delhi.lm.poi6)
```

